---
title: "Airbnb predictive pricing tool for tourists coming to Canada"
output: 
  github_document:
    toc: true
---

```{r, message=FALSE, include=FALSE}
library(tidyverse)
library(here)
```

```{r, message=FALSE, echo=FALSE, include=FALSE}
path = here::here("Data", "vancouver.csv")
data<-readr::read_csv(path)
```

## Introduction

According to Statistics Canada, a recording breaking **22.1 million international tourists from abroad visited Canada in 2019.** Hotels have always been the mainstay for accommodations but the prices can be unaffordable for visitors looking to stay long-term for tourism or work. Airbnb was founded in 2008 and has since been proven to be a successful online platform to match hosts with unused space with guests looking for an affordable place to lodge. Although it is often more affordable than hotels, Airbnb does not have a direct effect on the prices of lodging offered by hosts and leaves the hosts to decide the prices. In this analysis, we want to investigate which factors, ranging from the location of the listing to the number of bathrooms, are most likely influencing the price of Airbnb listings for cities in Canada. This predicitive tool may potentially help travellers better understand the reasoning behind the listed price of Canadian Airbnb listings. 

## Data Description


```{r}
data$id<-as.factor(data$id)
nlevels(data$id) 
```

There are 6181 listings. 

```{r}
data$host_id<-as.factor(data$host_id)
nlevels(data$host_id) #4261 hosts.
```

There are 4261 hosts.

Select useful variables.

```{r}
data <- data %>% 
  select(id, host_id, host_is_superhost, host_listings_count, neighbourhood_cleansed, property_type, room_type, accommodates, bathrooms, bedrooms, beds, price, weekly_price, monthly_price, security_deposit, cleaning_fee, guests_included, extra_people, minimum_nights, maximum_nights, review_scores_rating)
```

## Exploring the Dataset

**Barplot**

```{r}
barplot(table(data$room_type), main="Room Type Summary")
```

**Scatterplot**

```{r}
data$price <- as.numeric(gsub('[$,]', '', data$price))
plot(data$price, data$minimum_nights, main="Minimum Nights vs. Price", xlab="price", ylab="minimum nights")
```


# Research Question

In this analysis, we aim to investigate the influence of various factors on the price of Airbnb listings across various Canadian cities to see which ones are most likely to impact the listed price. 

# Plan of Action

We will first establish that the provided datasets by InsideAirbnb can be utilized by thoroughly ensuring there is less than 5-10% of missing data. Next, we will perform a linear regression analysis between the price of the Airbnb listing and the various factors provided in the datasets. 

# References

https://www150.statcan.gc.ca/n1/daily-quotidien/200221/dq200221b-eng.htm?indid=3635-2&indgeo=0