---
title: "Airbnb predictive pricing tool for tourists coming to Canada"
output: 
  github_document:
    toc: true
---

```{r package, message=FALSE, include=FALSE}
library(tidyverse)
library(here)
library(corrplot)
```

```{r data cleaning, message=FALSE, echo=FALSE, include=FALSE, eval = FALSE}
Vancouver <- readr::read_csv(here("Data", "Vancouver.csv"))
Montreal <- readr::read_csv(here("Data","Montreal.csv"))
New_Brunswick <- readr::read_csv(here("Data","New Brunswick.csv"))
Ottawa <- readr::read_csv(here("Data","Ottawa.csv"))
Quebec <- readr::read_csv(here("Data","Quebec.csv"))
Toronto <- readr::read_csv(here("Data","Toronto.csv"))
Victoria <- readr::read_csv(here("Data","Victoria.csv"))
Vancouver <- Vancouver %>% 
  select(id, host_id, host_is_superhost, city, property_type, room_type, accommodates, bathrooms, bedrooms, beds, cancellation_policy, price) %>% 
  mutate(city = "Vancouver")
Montreal <- Montreal %>% 
  select(id, host_id, host_is_superhost, city, property_type, room_type, accommodates, bathrooms, bedrooms, beds, cancellation_policy, price) %>% 
  mutate(city = "Montreal")
New_Brunswick <- New_Brunswick %>% 
  select(id, host_id, host_is_superhost, city, property_type, room_type, accommodates, bathrooms, bedrooms, beds, cancellation_policy, price) %>% 
  mutate(city = "New Brunswick")
Ottawa <- Ottawa %>% 
  select(id, host_id, host_is_superhost, city, property_type, room_type, accommodates, bathrooms, bedrooms, beds, cancellation_policy, price) %>% 
  mutate(city = "Ottawa")
Quebec <- Quebec %>% 
  select(id, host_id, host_is_superhost, city, property_type, room_type, accommodates, bathrooms, bedrooms, beds, cancellation_policy, price) %>% 
  mutate(city = "Quebec")
Toronto <- Toronto %>% 
  select(id, host_id, host_is_superhost, city, property_type, room_type, accommodates, bathrooms, bedrooms, beds, cancellation_policy, price) %>% 
  mutate(city = "Toronto")
Victoria <- Victoria %>% 
  select(id, host_id, host_is_superhost, city, property_type, room_type, accommodates, bathrooms, bedrooms, beds, cancellation_policy, price) %>% 
  mutate(city = "victoria")
cleaned_data <- rbind(Vancouver, Montreal, New_Brunswick, Ottawa, Quebec, Toronto, Victoria)
cleaned_data$price <- as.numeric(gsub('\\$|,', '', cleaned_data$price))
readr::write_csv(cleaned_data, here::here("Data", "cleaned_data.csv"))
```

## Introduction

According to Statistics Canada, a recording breaking **22.1 million international tourists from abroad visited Canada in 2019.** Hotels have always been the mainstay for accommodations but the prices can be unaffordable for visitors looking to stay long-term for tourism or work. Airbnb was founded in 2008 and has since been proven to be a successful online platform to match hosts with unused space with guests looking for an affordable place to lodge. Although it is often more affordable than hotels, Airbnb does not have a direct effect on the prices of lodging offered by hosts and leaves the hosts to decide the prices. In this analysis, we want to investigate which factors, ranging from the location of the listing to the number of bathrooms, are most likely influencing the price of Airbnb listings for cities in Canada. This predicitive tool may potentially help travellers better understand the reasoning behind the listed price of Canadian Airbnb listings. 

## Data Description

The [Data](https://github.com/STAT547-UBC-2019-20/group_3_mksm1228_sihaoyu1220/tree/master/Data) folder contains raw Airbnb listings data for Montreal, New Brunswick, Ottawa, Quebec, Toronto, Vancouver, and Victoria. The datasets were obtained from the [Inside Airbnb](http://insideairbnb.com/new-york-city/) project, conceived and compiled by Murray Cox and John Morrix in 2019. Each row represents a single listing with detailed information such as location, price, and rating score. The cleaned dataset can be assessed [here](https://github.com/STAT547-UBC-2019-20/group_3_mksm1228_sihaoyu1220/tree/master/Data/cleaned_data).  Some useful variables are summarized below: 

| Variable      | Type          | Description  |
| ------------- |:-------------:| -----|
| host_is_superhost | String  | whether the host is a super host (TRUE or FALSE). |
| city | String | City of the listing belongs to. One exception: New Brunswick is a Province. |
| property_type | String | Property type of the listing. |
| room_type | String | Room type: Entire Room, Hotel room, Private room, or Shared room. |
| accommodates | Int | The number of people that can be accommodated in the unit. |
| bathrooms | Int | The number of bathroom in the unit.|
| bedrooms | Int | The number of bedrooms in the unit. |
| beds | Int | The number of beds in the unit. |
| cancellation_policy | String | Strictness of the cancellation policy. |
| price | Int | Price per night. |

## Exploring the Dataset

First we read in the dataset.

```{r load data, message=FALSE}
data <- readr::read_csv(here("Data", "cleaned_data.csv"))
```

### 1. Bar Chart

The barplot below shows the number of listings in different cities. From the plot, we can see that Toronto has the most number of listings (23397) and New Brunswick has the least number of listings (2227).

```{r}
data %>% 
  ggplot(aes(x = city))+
  geom_bar(stat="count")+
  labs(x = "City", y = "Count", title = "Number of Listings by City") + 
  geom_text(stat='count',aes(label=..count..), vjust=-0.3, size=3.5) + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
```

### 2. Proportional Bar Chart

The proportional bar chart below shows the percentage of superhost in different cities. From the plot, Victoria seems to have the largest percentage of suphosts (almost 50\%), while Montreal seems to have the smallest percentage of superhosts (less than 25\%).

```{r, message=FALSE}
host <- distinct(data, host_id, .keep_all = TRUE)
host %>% 
  filter(host_is_superhost == TRUE | host_is_superhost == FALSE) %>% 
  ggplot()+
  geom_bar(mapping = aes(x=city, fill = host_is_superhost),
           position = "fill")+
  ylab("Proportion of superhost")+
  xlab("City")+
  ggtitle("Proportion of Superhosts by City")+
  scale_fill_brewer(name = "Superhost", palette="Paired")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5))
```

### 3. Correllogram 

From the correllogram below, there is a strong relationship between the number of accommodates and the number of beds in the unit. This may result a problem when doing linear regression because some predictors are collinear. To solve the collinearity problem, we may not use all of the variables (accommodates, bathrooms, bedrooms, and beds) as predictors in the linear regression model.

```{r}
data[7:10] <- sapply(data[7:10] , as.double)
corr <- cor(na.omit(data[7:10]))
corrplot(corr, method="color", tl.srt=0,type="lower",
         title = "Correlation between room facilities")
```

### 4. Side-by-side boxplots

The side-by-side boxplots shows the price per night (after log10 transformation) distribution in different cities. From the plots, we can see that there are some extremely high prices in the dataset. In later analysis, we need to figure out the reason for the extreme prices. Otherwise, we need to delete the extreme points as outliers.

```{r, warning=FALSE}
ggplot(data)+geom_boxplot(aes(city, log10(price), group = city))
```


# Research Question

In this analysis, we aim to investigate the influence of various factors on the price of Airbnb listings across various Canadian cities to see which ones are most likely to impact the listed price. 

# Plan of Action

We will first establish that the provided datasets by InsideAirbnb can be utilized by thoroughly ensuring there is less than 5-10% of missing data. Next, we will perform a linear regression analysis between the price of the Airbnb listing and the various factors provided in the datasets.

Martin

# References

https://www150.statcan.gc.ca/n1/daily-quotidien/200221/dq200221b-eng.htm?indid=3635-2&indgeo=0